\section{Features} In this section, we will provide the details about certain features of the application.

\paragraph{\textbf{Performance}} The application is built in React and is integrated with Firebase.The performance of the application is fast and user-friendly. Users can navigate between different sections of the application with ease.

\paragraph{\textbf{Reliability}} The application delivers correct output to the user from start to end. Users can retrieve any stored paper with ease and add comments for further review and update it accordingly. The application delivers what it needs to perform and asks inputs accordingly so that it can work accordingly.

\paragraph{\textbf{Availability}} The application is free to use for any users. As the application is designed keeping in view of various users where they can store their research work and retrieve for further use. Users can create an account and login with their credentials, upload and retrieve papers for further use.

\paragraph{\textbf{Security}} The application is protected with authentication provided by Firebase where it doesn’t allow other users to use some others account until and unless the login credentials are misused. Firebase has various inbuilt authentication steps to register or login just by enabling and using the features in code.

\paragraph{\textbf{Portability}} Currently, the application is designed as web application. The application runs on server side so there is no restriction for any systems other than mobile devices.


